Strings functions analysis

### 2022-08-22 article.tex
all research methods wrapped by one

    \section{Considered functions}

@@

    \section{Popularity of functions}

    \subsection{Definition}

@@

    \subsection{Search algorithm}

@@

    \section{Mutual usages}

@@

    \section{Asymptotics}

    \subsection{Mutable}

@@

    \subsection{Immutable}

@@

    \section{Finding the minimum set}

    \subsection{Necessity}

@@

    \subsection{Parameter setting}

@@

    \subsection{Algorithm}

@@

    \begin{enumerate}
        \item Set is initially empty.
        \item Functions are considered in priority order, by default the most popular functions come first. If the function meets criterion 7.2, it is added to the set.
        \item The second step is repeated until there are no unselected functions left.
        \item In reverse order of priority the functions in the set are considered and those that don't meet criterion 7.2 are removed.
    \end{enumerate}

>>>>

    \section{Research Method}

    \subsection{Considered functions}

@@

    \subsection{Popularity of functions}

    \subsubsection{Definition}

@@

    \subsubsection{Search algorithm}

@@

    \subsection{Mutual usages}

@@

    \subsection{Asymptotics}

    \subsubsection{Mutable}

@@

    \subsubsection{Immutable}

@@

    \subsection{Finding the minimum set}

    \subsubsection{Necessity}

@@

    \subsubsection{Criterion setting}

@@

    \subsubsection{Algorithm}

@@

    \begin{enumerate}
        \item Set is initially empty.
        \item Functions are considered in priority order, by default the most popular functions come first. If the function meets criterion 3.5.2, it is added to the set.
        \item The second step is repeated until there are no unselected functions left.
        \item In reverse order of priority the functions in the set are considered and those that don't meet criterion 3.5.2 are removed.
    \end{enumerate}
